```{r, echo=FALSE, warning = FALSE}


```
\section*{\textbf{\underline{Standard Curve (Set `r index`)}}}

\subsection*{\textbf{Experiment Information}}

\begin{tabular}{l l}
File name: &  `r file_name` \\
Run started & `r run_started` \\
Run ended & `r run_ended` \\
Machine used: & `r machine` \\
\end{tabular}

\subsection*{\textbf{Quantification Information}}

\begin{tabular}{|c | c | c |}
\hline
Parameter & Results & QC Status \\
\hline
Threshold &   `r threshold`    &     -    \\
Slope     &  `r slope`       &   `r albumin_status1`        \\
Reaction efficiency &  `r reaction_efficiency`  &  -      \\
$R^2$ Value   &   `r r_2_value`      &      `r albumin_status2`     \\
\hline
\end{tabular} 

\subsection*{\textbf{Quantification Results} }

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{`r figure_path`}
    \label{fig:yourlabel}
\end{figure}

```{r , fig.align="center", echo = FALSE}

 
kbl(display,
    format = "latex",
    booktabs = TRUE,
    escape = FALSE,
    align = "l", 
    linesep = "") 




```



\subsection*{\textbf{Quality Control (QC) Checklist}}


\begin{tabularx}{\textwidth} {|c | X | c|}
\hline
\textbf{No.} & \textbf{Quality Control Criteria} & \textbf{QC Status} \\
\hline
1   & Slope between -2.9 and -3.9 &     `r albumin_status1`   \\
2   & $R^2$ value: $\geq$0.97     &     `r albumin_status2`  \\
3   & $\Delta$Ct of replicates within $\pm$1.5 &   `r albumin_status3` \\
4   & $\Delta$Ct of Average Ct between consecutive 10-fold dilution: 2.6 to 4.0 & `r albumin_status4` \\
5   & NTC: Calculated Concentration <10 or Ct $\geq$40     &  `r albumin_status5` \\
\hline
\multicolumn{2}{|l}{Overall QC Status}   &  `r overall_albumin_qc_status` \\
\hline
\end{tabularx}

\newpage  
