```{r, echo=FALSE, warning = FALSE}


```
\textbf{\underline{Standard Curve (Set `r index`)}}

\textbf{Experiment Information}

\begin{tabular}{l l}
File name: &  `r file_name` \\
Run started & `r run_started` \\
Run ended & `r run_ended` \\
Machine used: & `r machine` \\
\end{tabular}

\textbf{Quantification Information}

\begin{tabular}{|c | c | c |}
\hline
Parameter & Results & QC Status \\
\hline
Threshold &   `r threshold`    &     -    \\
Slope     &  `r slope`       &   `r slope_status`        \\
Reaction efficiency &  `r reaction_efficiency`  &  `r reaction_efficiency_status`      \\
$R^2$ Value   &   `r r_2_value`      &      `r r_2_status`     \\
\hline
\end{tabular} 

\textbf{Quantification Results} 

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{`r figure_path`}
    \label{fig:yourlabel}
\end{figure}

```{r , fig.align="center", echo = FALSE}

 
kbl(display,
    format = "latex",
    booktabs = TRUE,
    escape = FALSE,
    align = "l", 
    linesep = "") 




```



\textbf{Quality Control (QC) Checklist}


\begin{tabularx}{\textwidth} {|c | X | c|}
\hline
\textbf{No.} & \textbf{Quality Control Criteria} & \textbf{QC Status} \\
\hline
1   & Slope between -3.1 and -3.6 &     `r slope_status`   \\
2   & Reaction Efficiency 90\%-110\% &  `r reaction_efficiency_status`     \\
3   & $R^2$ value: $\geq$0.99     &     `r r_2_status`  \\
4   & $\Delta$Ct of replicates within $\pm$1.5 &   `r replicate_status` \\
5   & $\Delta$Ct of Average Ct between consecutive Standards: 3.1 to 3.6 & `r average_status` \\
6   & Lowest Ct of NTC $\geq$3.0 Ct from highest Ct of Standard 6       &  `r status6` \\
\hline
\multicolumn{2}{|l}{Overall QC Status}   &  `r overall_qc_status` \\
\hline
\end{tabularx}

\newpage  
